Fare Calculator

### 2022-02-21 r-package/tests_marcus/fare_calculator.Rmd
Many changes in fare calculator feature: - fares now accept float values, which are automatically converted to integer for R5 compatibility; - JSON serialisation is now made using Jackson; - removed support for other fare calculators (only RuleBasedFareCalculator is allowed) - function `set_fare_calculator()` created in fare_calculator.R, to pass fare_calculator_settings from R to Java - added fare calculator feature to `travel_time_matrix()` - lots of code cleanup

```{r}
fare_settings <- setup_fare_calculator(r5r_core, 
                                       base_fare = 480,
                                       by = "MODE")
```

@@

```{r}
fare_settings$fare_per_mode
```

@@

```{r}
fare_settings$fare_per_mode[mode == "RAIL", unlimited_transfers := TRUE]
fare_settings$fare_per_mode[mode == "RAIL", fare := 450]
fare_settings$fare_per_mode[mode == "BUS", allow_same_route_transfer := FALSE]
```

@@

```{r}
fare_settings$fare_per_transfer
```

@@

```{r}
fare_settings$fare_per_transfer[leg1 == "BUS" & leg2 == "BUS", 
                                fare := 720]
```

@@

```{r}
fare_settings$fare_per_transfer <- 
  fare_settings$fare_per_transfer[!(leg1 == "RAIL" & leg2 == "RAIL")]
```

@@

```{r}
fare_settings$fare_per_transfer[leg1 != leg2, fare := 837]
```

@@

```{r}
tail(fare_settings$routes_info)
```

@@

# helper function to calculate accessibility with common settings
calculate_accessibility <- function(settings, fare) {
  if (!is.null(settings)) {
    debug_file <- here::here("tests_marcus/debug_poa", 
                             paste0("debug_fare_", fare, ".csv" ))
    settings$debug_settings$output_file = debug_file
  }

@@

```{r}
access_unl <- calculate_accessibility(NULL, 0)
access_300 <- calculate_accessibility(fare_settings, 300)
access_500 <- calculate_accessibility(fare_settings, 500)
access_900 <- calculate_accessibility(fare_settings, 900)
```

>>>>

```{r}
fare_settings <- setup_fare_calculator(r5r_core, 
                                       base_fare = 4.8,
                                       by = "MODE")
```

@@

```{r}
fare_settings$fares_per_mode
```

@@

```{r}
fare_settings$fares_per_mode[mode == "RAIL", unlimited_transfers := TRUE]
fare_settings$fares_per_mode[mode == "RAIL", fare := 4.5]
fare_settings$fares_per_mode[mode == "BUS", allow_same_route_transfer := FALSE]
```

@@

```{r}
fare_settings$fares_per_transfer
```

@@

```{r}
fare_settings$fares_per_transfer[first_leg == "BUS" & second_leg == "BUS", 
                                fare := 7.2]
```

@@

```{r}
fare_settings$fares_per_transfer <- 
  fare_settings$fares_per_transfer[!(first_leg == "RAIL" & second_leg == "RAIL")]
```

@@

```{r}
fare_settings$fares_per_transfer[first_leg != second_leg, fare := 8.37]
```

@@

```{r}
tail(fare_settings$fares_per_route)
```

@@

# helper function to calculate accessibility with common settings
calculate_accessibility <- function(settings, fare) {

  if (!is.null(settings)) {
    settings$debug_settings$output_file = 
      here::here("tests_marcus", paste0("debug_fare_", fare, ".csv" ))
  }

  # if (!is.null(settings)) {
  #   debug_file <- here::here("tests_marcus/debug_poa", 
  #                            )
  #   settings$debug_settings$output_file = debug_file
  # }

@@

```{r}
access_unl <- calculate_accessibility(NULL, 0)
access_300 <- calculate_accessibility(fare_settings, 3.00)
access_500 <- calculate_accessibility(fare_settings, 5.00)
access_900 <- calculate_accessibility(fare_settings, 9.00)
```

```{r}
clipr::write_clip(r5r_core$getFareStructure())
clipr::write_clip(r5r_core$getFareCalculatorDebugOutputSettings())
r5r_core$setFareCalculatorDebugOutputSettings(here::here("tests_marcus", "dbg2.csv"),
                                              "MODE")
```
